### 2023-04-13 Notes/nonmonotone_project.tex
Wrote double robustness.

    \item \textbf{Analyzed simulation from monotone MAR}:
    Following the algorithm described in the monotone MAR simulation bullet, 
    we first generate data from the following distributions:
    \begin{align*}
        X_i &\stackrel{iid}{\sim} N(0, 1) \\
        Y_{1i} &\stackrel{iid}{\sim} N(0, 1)\\
        Y_{2i} &\stackrel{iid}{\sim} N(\theta, 1)
    \end{align*}

@@

    We run this simulation with different values of $\theta$, sample size of 1000, and
    1000 Monte Carlo replications. Each algorithm for each replication generates
    $\hat \theta$. In the subsequent tables, we compute the bias, standard deviation (sd),
    t-statistic (where we test for a significant difference between the Monte Carlo
    mean $\hat \theta$ and the true $\theta$) and the p-value of the t-statistic.

@@

    \item \textbf{Analyzed simulation from nonmonotone MAR}:
    Like the monotone simulation, we generate data using:
    \begin{align*}
        X_i &\stackrel{iid}{\sim} N(0, 1) \\
        Y_{1i} &\stackrel{iid}{\sim} N(0, 1)\\
        Y_{2i} &\stackrel{iid}{\sim} N(\theta, 1)
    \end{align*}

    However, because we have nonmonotone data, our ``Stage 1'' probabilities are
    different. We compute the true Stage 1 probabilities being proportional to the
    following values:

    \begin{align*}
        p_0 &\propto |x - 2|\\
        p_1 &\propto |x|\\
        p_2 &\propto |x + 2|.
    \end{align*}

@@

    \input{../Tables/nonmonomar_t-5}
    \input{../Tables/nonmonomar_t0}
    \input{../Tables/nonmonomar_t5}

    \newpage
\end{itemize}

\section*{Todo:}

\begin{itemize}
    \item \textbf{Estimate IPW probabilities for nonmonotone MAR}:
\end{itemize}

>>>>

  \item \textbf{Simulation 1 with Monotone MAR}:
    Following the algorithm described in the monotone MAR simulation bullet, 
    we first generate data from the following distributions:
    \begin{align*}
        X_i &\stackrel{iid}{\sim} N(0, 1) \\
        Y_{1i} &\stackrel{iid}{\sim} N(0, 1)\\
        Y_{2i} &\stackrel{iid}{\sim} N(\theta, 1)
    \end{align*}

@@

    We run this simulation with different values of $\theta$, sample size of
    2000, and 2000 Monte Carlo replications. Each algorithm for each replication
    generates $\hat \theta$. In the subsequent tables, we compute the bias,
    standard deviation (sd), t-statistic (where we test for a significant
    difference between the Monte Carlo mean $\hat \theta$ and the true $\theta$)
    and the p-value of the t-statistic.

@@

    \item \textbf{Simulation 1 with Nonmonotone MAR}:

    We generate variables $(X, Y_1, Y_2)$ using the following setup:

    \[\begin{bmatrix}
    X_i \\ \varepsilon_{1i} \\ \varepsilon_{2i}
    \end{bmatrix} \stackrel{iid}{\sim}
    N\left(
    \begin{bmatrix}
        0 \\ 0 \\ \theta
    \end{bmatrix},
    \begin{bmatrix}
        1 & 0 & 0 \\
        0 & 1 & \sigma_{yy}\\
        0 & \sigma_{yy} & 1
    \end{bmatrix}
    \right).\]

    Then,

    \[y_{1i} = x_i + \varepsilon_{1i} \text{ and } 
    y_{2i} = x_i + \varepsilon_{2i}.\]

    Since we have nonmonotone data, our ``Stage 1'' probabilities are
    different. We compute the true Stage 1 probabilities being proportional to
    the following values:

    \begin{align*}
        p_0 &= 0.2 \\
        p_1 &= 0.4 \\
        p_2 &= 0.4 \\
    \end{align*}

@@

    \input{Tables/nonmonocmar_t-5cy1y20.tex}
    \input{Tables/nonmonocmar_t0cy1y20.tex}
    \input{Tables/nonmonocmar_t5cy1y20.tex}

    \item \textbf{Simulation 2 with Nonmonotone MAR}:
    We also want to simulate data that is correlated. For this simulation, we
    focus on $\Cov(Y_1, Y_2)$. The data generating process now has $\sigma_{yy}
    \neq 0$. We are still interested in $\bar Y_2$ and we still run 2000
    simulation with 2000 observations. In all of the next simulations the true
    value of $\theta = 0$. The results are the following:

    \input{Tables/nonmonocmar_t0cy1y20.1.tex}
    \input{Tables/nonmonocmar_t0cy1y20.5.tex}
    \input{Tables/nonmonocmar_t0cy1y20.9.tex}

  \item \textbf{Simulation 3 with Nonmonotone MAR}:
    This simulation aims to see if the proposed algorithm is doubly robust.
    First, we check with a misspecified outcome model. In this case the data
    generating procedure is the following:

    \[\begin{bmatrix}
    X_i \\ \varepsilon_{1i} \\ \varepsilon_{2i}
    \end{bmatrix} \stackrel{iid}{\sim}
    N\left(
    \begin{bmatrix}
        0 \\ 0 \\ \theta
    \end{bmatrix},
    \begin{bmatrix}
        1 & 0 & 0 \\
        0 & 1 & \sigma_{yy}\\
        0 & \sigma_{yy} & 1
    \end{bmatrix}
    \right).\]

    Then,

    \[y_{1i} = x_i + x_i^2 \varepsilon_{1i} \text{ and } 
    y_{2i} = -x_i + x_i^3 + \varepsilon_{2i}.\]

    This procedure causes $X$ to influence both $Y_1$ and $Y_2$ and we still
    have correlation in the error terms of $Y_1$ and $Y_2$. However, since
    neither $Y_1$ nor $Y_2$ are linear in $X$, the model will be misspecified.
    The response mechanisms are first generated MCAR with a probability of
    either $Y_1$ or $Y_2$ being the first variable observed to be $0.4$. (There
    is a $0.2$ probability neither is observed.) Then the probability of the
    other variable being observed is proportional to $\logistic(y_k)$ where
    $y_k$ is the $y$ that has been observed. To ensure that the proposed method
    has the correct propensity score we use the oracle probabilites instead of
    estimating them. This yields the following:

    \input{Tables/nmonocmar_t0cy1y20.tex}
    \input{Tables/nmonocmar_t0cy1y20.1.tex}
    \input{Tables/nmonocmar_t0cy1y20.5.tex}

    Clearly, the proposed method is unbiased with a misspecified outcome model.
    When the response model is misspecified as in Simulation 1, the procedure
    still works.

\end{itemize}

{\bf Commments from JK}
\begin{itemize}
    \item Three variables $(X, Y_1, Y_2)$ should be correlated. 
\end{itemize}
